\documentclass[titlepage]{jsarticle}

\usepackage{here}
\usepackage{array,booktabs} %表のためのarray環境
%数式用パッケージ
\usepackage{amsmath,amssymb}
\usepackage{mathtools}
\usepackage{cancel}
\usepackage{cases}
\usepackage{bm}
\usepackage{colortbl}
\usepackage{float}
\usepackage{subcaption}
%ファインマングラフ用パッケージ
\usepackage{feynmf}
%ハイパーリンクの設定
\usepackage[dvipdfmx]{graphicx}
\usepackage[dvipdfmx]{hyperref}
\usepackage{pxjahyper}
\hypersetup{
  colorlinks=false, % リンクに色をつけない設定
  bookmarks=true, % 以下ブックマークに関する設定
  bookmarksnumbered=true,
  pdfborder={0 0 0},
  bookmarkstype=toc
}

\newcommand{\Slash}[1]{{\ooalign{\hfil/\hfil\crcr\(#1\)}}}
\newcommand{\figref}[1]{\figurename\ref{#1}}
\newcommand{\tabref}[1]{\tablename\ref{#1}}

%\graphicspath{{./figure/}}

\begin{document}
%title
\title{課題研究P2\\J-PARC MLF  のミューオンビームを用いた\\ミューオン崩壊に関する諸量の測定}
\author{阿部倫史，池満拓司，小田川高大，田島正規\\羽田野真友喜，早川龍，三野裕哉}
\date{\today}
\maketitle
%目次
\tableofcontents
\newpage
%
% 句読点の統一
\include{report_abe}
\include{hayakawa_1st}
\include{tajima_1st}
\include{report_ike}
\include{odagawa_1st}
\include{mino_1st}
\include{hatano_1st}
\include{conclusion}
\include{acknowledgment}
\newpage
%Appendix
\appendix
\include{lifetime}
\include{lsm}
%参考文献(APA Style)
\begin{thebibliography}{99}
% URL List
\bibitem{aboutmuon} Ultra Slow Muon - J-PARC MLF MUSE. (n.d.). Retrieved May 31, 2018
  from \url{http://slowmuon.kek.jp/aboutMuon.html}
\bibitem{g-2_experiment} Fundamental Physical Constants from NIST. (n.d.). Retrieved May 31, 2018
  from \url{https://physics.nist.gov/cuu/Constants/index.html}
\bibitem{magnet} 加速器用超伝導磁石 - KEK. (n.d.). Retrieved May 31, 2018
  from \url{http://accwww2.kek.jp/oho/OHO\%20text\%20archives\%202005-2011/OHO11\%20web\%20final/OHO11\%20ogitsu\%2020110906.pdf}
\bibitem{Hamamatsu_PMT} 光電子増倍管ハンドブック - 浜松ホトニクス. (n.d.) Retrieved May 31, 2018
  from \url{https://hamamatsu.hpk.co.jp/pmt_handbook_g?\_ga=2.233766876.379427155.1527087385-2128085973.1527087385}
\bibitem{IAEA_ENSDF} Evaluated Nuclear Structure Data File Search and Retrieval - IAEA. (n.d.) Retrieved May 31, 2018
  from \url{http://www.nndc.bnl.gov/ensdf/}
  
% Book List
\bibitem{leo} Leo, W. R. (1994). \textit{Techniques for Nuclear and Particle Physics Experiments: A How-to Approach}. Berlin: Springer-Verlag GmbH.
\bibitem{Mandl} Mandl, F., \& Shaw, G. (2010). \textit{Quantum Field Theory}. New York: John Wiley \& Sons Inc.

% Artcile List
\bibitem{PDG} Patrignani, C., \&  Particle Data Group (2016). Review of Particle Physics. \textit{Chinese Physics C}, 40 (10), 100001.
\bibitem{michel_parameter} Bayes, R., \& TWIST collaboration (2011). Experimental Constraints on Left-Right Symmetric Models from Muon Decay. \textit{Physical Review Letters}, 106 (4), 041804.
\bibitem{michel_interaction} Kinoshita, T., \& Sirlin, A. (1957). Muon Decay with Parity Nonconserving Interactions and Radiative Corrections in the Two-Component Theory. \textit{Physical Review}, 107 (2), 593-599.
\bibitem{g-2_thory} Hagiwara, K., Martin, A. D., Nomura, D., \& Teubner, T. (2007). Improved predictions for $g-2$ of the muon and $\alpha_{QED}({M_Z}^2)$. \textit{Physics Letters B}, 649 (2-3), 173-179.
  
\end{thebibliography} 

\end{document}
